

## samples

The authors used nasal airway epithelial cells (NAECs) from 2–3-year-old children in the INSPIRE birth cohort, stratified into four groups: control, RSV-only (infant infection, no wheeze), wheeze-only, and wheeze plus RSV. NAECs were expanded and differentiated at the air-liquid interface (ALI) for 3 weeks, then profiled by scRNA-seq. The samples can be found in this link NCBI GEO repository (accession number GSE286262). The samples are shown in the table below.

```{r (Table1: Summary of the Samples)}
setwd("D:/May_journal")

readxl::read_xlsx("data/ss.xlsx")
```

## Integration

What I found interesting about this analysis is that they seemed to try two integration methods in two different contexts: Seurat integration (CCT) to integrate samples, followed by Harmony integration to integrate "groups". I decided to run both methods and compare the PCA plots, and the UMAP plote

Pre-integration PCA plot shows seperation of samples as shown below.

```{r (Fig.1 Pre-integration PCA)}
pca_preint <- DimPlot(sc_merge_unint,
                      reduction = "unintegrated_pca",
                      group.by = "orig.ident")

pca_preint_group <- DimPlot(sc_merge_unint,
                            reduction = "unintegrated_pca",
                            group.by = "group")
print(pca_preint + pca_preint_group)& theme( axis.text = element_blank(),
                                             axis.ticks = element_blank(),
                                             axis.title = element_text(size = 12),
                                             text = element_text(size = 12, family = "ArialMT"))&
  ggtitle("Pre-integration PCA")
```

While both seurat based integration and Harmony result in a similar PCA plot (Fig.2), the umap appears superior in correcting the batch effect (Fig.3). So I decided to proceed with harmony.

```{r (Fig.2 PCA in Harmony)}

p1 <- (pca_int + pca_int_group) &
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 12),
    text = element_text(size = 12, family = "ArialMT")
  )

p1 <- p1 & ggtitle( "CCA Seurat-based integration")

p2 <- (pca_harmony + pca_harmony_group) &
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 12),
    text = element_text(size = 12, family = "ArialMT")
  )

p2 <- p2 & ggtitle("Harmony integration")

print(p1/p2)


```

```{r}
p1 <- DimPlot(sc.data, reduction = "umap", group.by = "orig.ident")& theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 12),
    text = element_text(size = 12, family = "ArialMT")
  )&ggtitle("Harmony integration") 
p2 <- DimPlot(Int, reduction = "umap", group.by = "orig.ident")& theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 12),
    text = element_text(size = 12, family = "ArialMT")
  )&ggtitle("CCA Seurat-based integration") 
  
  print(p1+p2)

```
